---
title: "HW 1 document"
output: github_document
---
run the library
```{r}
library(ggplot2)
library(tidyverse)
```

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

load the penguins dataset first

```{r}
str(penguins)
nrow_penguins <- nrow(penguins)
ncol_penguins <- ncol(penguins)
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```
we first find the measurements for three species of penguins. Key variables include:

species: The species of the penguin

island: The island where the penguin was observed

bill_length_mm: The length of the penguin’s bill 

flipper_length_mm: The length of the penguin’s flipper 

We can clearly see that this dataset has 8 variables and 344 observation which mean it has 8 col and 344 row.

we also find that the mean of flipper_length_mm is `r mean_flipper_length`



Finally make a scatter plot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)") +
  theme_minimal()
```


# Problem 2

Generate the data(I did not create seed)
```{r}
normal_sample <- rnorm(10)
logical_vector <- normal_sample > 0
character_vector <- letters[1:10]  # first 10 letters
factor_vector <- factor(rep(c("Level1", "Level2", "Level3"), length.out = 10))

```

Create a data frame
```{r}
df <- data.frame(
  normal_sample = normal_sample,
  logical_vector = logical_vector,
  character_vector = character_vector,
  factor_vector = factor_vector
)

```
 
Try to take the mean of each variable

```{r warning=FALSE}
normal_mean <- mean(pull(df, normal_sample))
logical_mean <- mean(pull(df, logical_vector))
character_mean <- mean(pull(df, character_vector))  
factor_mean <- mean(pull(df, factor_vector))
```

we can calculate the mean of normal_sample and logical_vector, but it failed on character_vector and factor_vector.
here is the output of mean: normal_mean-`r normal_mean`, logical_mean-`r logical_mean`, character_mean-`r character_mean`, factor_mean-`r factor_mean`

Coerce logical, character, and factor variables to numeric
```{r eval = FALSE}
logical_as_numeric <- as.numeric(df$logical_vector)
character_as_numeric <- as.numeric(df$character_vector)
factor_as_numeric <- as.numeric(df$factor_vector)

```
Only character is failed to convert. 
The logical vector will be converted to 1 for TRUE and 0 for FALSE.
The character can not convert to number.
The Factors will be converted to integers.
It does explain the what happens when I try to take mean, because the factor need one more  step to convert it to integer.










