---
title: "HW 1 document"
output: github_document
---
run the library
```{r}
library(ggplot2)
```

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

load the penguins dataset first

```{r}
str(penguins)
nrow_penguins <- nrow(penguins)
ncol_penguins <- ncol(penguins)
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```
we first find the measurements for three species of penguins. Key variables include:

species: The species of the penguin

island: The island where the penguin was observed

bill_length_mm: The length of the penguin’s bill in millimeters

flipper_length_mm: The length of the penguin’s flipper in millimeters

We can clearly see that this dataset has 8 variables and 344 observation which mean it has 8 col and 344 row.

we also find that the mean of flipper_length_mm is `r mean_flipper_length`

Finally make a scatter plot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)") +
  theme_minimal()
```


# Problem 2


